Paper on the carbonate chemistry at Ny-Ålesund

### 2020-03-12 paper.Rmd
added one plotly plot

---
title: "Paper on the carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso, Samir Alliouane and Philipp Fischer"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
#library(reshape2)
library(lubridate)
#library(lmtest)
#library(grid)
library(viridis)
#library(dygraphs)
require("knitr")
library("lmodel2")
#library(captioner)
#library(xts)
#library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

@@

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

@@

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        #aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(
  readRDS(file = paste0(path, "fb_data/d_all.rds"))
) %>%
  filter(sal_fb > 28) # remove salinity data lower than 28
```

## Whole time series
```{r whole time series, fig.width=10, fig.height=15, echo=FALSE, message= FALSE}
size_point <- 1 # size of data points

#SAL SBE45
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
  #coord_fixed() +
  Mytheme(size_labs = 8)

@@

```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
  #scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) #+
  #theme(axis.text.x=element_blank())
#  +annotation_custom(grob_A)
print(temp_sal)

```

>>>>

---
title: "Paper on the carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso, Samir Alliouane and Philipp Fischer"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false
fig_width: 12 
fig_height: 8     
---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
library(lubridate)
#library(lmtest)
#library(grid)
library(viridis)
#library(dygraphs)
require("knitr")
library("lmodel2")
#library(captioner)
#library(xts)
#library(seismicRoll)
library(scales)
library(plotly)
library(htmlwidgets)
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = normalizePath("/Users/gattuso/not_synced_git/AWIPEV-CO2-git"))

#knitr::opts_chunk$set(fig.width=12, fig.height=8)

@@

#define who is the user and define paths
if (Sys.getenv("LOGNAME") == "gattuso") path_data = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "gattuso") path_fig = "/Users/gattuso/pCloud\ Sync/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/figures/"
if (Sys.getenv("LOGNAME") == "samir") path_data = "../../pCloud\ Sync/exp168_awipev-CO2/"

@@

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        #aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(
  #readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
  readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
) %>%
  filter(sal_fb > 28) # remove salinity data lower than 28
```

## Whole time series
```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
size_point <- 1 # size of data points

#SAL SBE45
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
  #coord_fixed() +
  Mytheme(size_labs = 8)
ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
filename.html <- paste0(path_fig, "ts_sal_py.html")
saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")

@@

```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) #+
  #theme(axis.text.x=element_blank())
#  +annotation_custom(grob_A)
print(temp_sal)

den <- seacarb::rho(S = d_all$sal_fb , T = d_all$temp_insitu, P = 1)
d_all <- d_all %>%
  dplyr::mutate(den = den)
ts_den <- d_all %>%
  ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Density",x="Time", y="Density") +
  #coord_fixed() +
  Mytheme(size_labs = 8)
print(ts_den)
```
